---
title: "Function Maximization"
author: "Samuel Wilson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Function Maximization}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
options(width = 1000)
set.seed(1991)
```

********
## Simple Example  
Bayesian Optimization seek the global maximum of any user defined function. As a simple example, let's define a simple function:
```{r eval = TRUE, echo = TRUE, message = FALSE,fig.height=4,fig.width=4}
library(ggplot2)
library(ParBayesianOptimization)
simpleFunction <- function(x) dnorm(x,3,2)*1.5 + dnorm(x,7,1) + dnorm(x,10,2)
maximized <- optim(8,simpleFunction,method = "L-BFGS-B",lower = 0, upper = 15,control = list(fnscale = -1))$par
ggplot(data = data.frame(x=c(0,15)),aes(x=x)) + 
  stat_function(fun = simpleFunction) +
  geom_vline(xintercept = maximized,linetype="dashed")
```  

We can see that this function is maximized around x~7.023. We can use ```bayesOpt``` to find the global maximum of this function. We just need to define the bounds, and the initial parameters we want to sample:

```{r}
bounds <- list(x=c(0,15))
initGrid <- data.frame(x=c(0,5,10))
```

Here, we run ```bayesOpt```. The function begins by running ```simpleFunction``` 3 times, and then fits a Gaussian process to the results in a process called [Kriging](https://en.wikipedia.org/wiki/Kriging). We then calculate the ```x``` which maximizes our expected improvement, and run ```simpleFunction``` at this x. We then go through 1 more iteration of this:
```{r}
FUN <- function(x) list(Score = simpleFunction(x))
optObj <- bayesOpt(
  FUN = FUN
  , bounds = bounds
  , initGrid = initGrid
  , acq = "ei"
  , iters.n = 2
  , gsPoints = 25
)
```  

Let's see how close the algorithm got to the global maximum:
```{r}
getBestPars(optObj)
```  

The process is getting pretty close! We were only about 12% shy of the global optimum:
```{r}
simpleFunction(7.023)/simpleFunction(getBestPars(optObj)$x)
```

Let's run the process for a little longer:
```{r}
optObj <- addIterations(optObj,iters.n=2,verbose=0)
simpleFunction(7.023)/simpleFunction(getBestPars(optObj)$x)
```  

We have now found an ```x``` very close to the global optimum. 


